---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# norSTR

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/norSTR)](https://CRAN.R-project.org/package=norSTR)
[![](https://cranlogs.r-pkg.org/badges/grand-total/norSTR?color=yellow)](https://cran.r-project.org/package=norSTR)
[![](https://cranlogs.r-pkg.org/badges/last-month/norSTR?color=yellow)](https://cran.r-project.org/package=norSTR)
<!-- badges: end -->

The **norSTR** package contains a genetic map of 51 autosomal STR markers and allele frequency databases for several populations. The marker panel includes the CODIS core loci and markers from commercial kits such as Fusion 6C and SureID27.

Details and references for the physical positions are provided in
[`data-raw/STR51_GRCh38_positions.xlsx`](data-raw/STR51_GRCh38_positions.xlsx).
Genetic positions were obtained from these coordinates using
`ibdsim2::convertPos()`, based on the recombination map of Halldorsson et al.
(2019). Allele frequency databases were compiled from published sources and
in-house data.

These databases are maintained and used for kinship analysis by the Department of
Forensic Sciences in Oslo, Norway. The **norSTR** package is used by [KLINK](https://cran.r-project.org/package=KLINK) and other packages in the [pedsuite](https://magnusdv.github.io/pedsuite/) ecosystem.


### Populations included:

- Norway (50 markers)
- Europe (45 markers)
- Africa (48 markers)
- South America (32 markers)
- East Asia (40 markers)
- Middle Asia (48 markers)
- West Asia (50 markers)

A minimum allele frequency of 0.001 was applied in all databases. 
Frequencies below this threshold were adjusted to 0.001.

### Marker map

The current map contains physical and genetic positions of 51 markers:

```{r}
norSTR::map51
```

### Marker subsets

For convenience, the package provides subsets of markers corresponding to widely-used kits and panels:

```{r}
norSTR::markerSets
```

### Installation

The package can be installed from CRAN with the following command:
```{r, eval = F}
install.packages("norSTR")
```
