---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# norSTR

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/norSTR)](https://CRAN.R-project.org/package=norSTR)
[![](https://cranlogs.r-pkg.org/badges/grand-total/norSTR?color=yellow)](https://cran.r-project.org/package=norSTR)
[![](https://cranlogs.r-pkg.org/badges/last-month/norSTR?color=yellow)](https://cran.r-project.org/package=norSTR)
<!-- badges: end -->

Allele frequency databases for forensic short tandem repeat (STR) markers. 
The package provides allele frequency data for 50 markers, 
including markers from the `Fusion 6C` and `SureID` kits, among others.
These databases are maintained and used for kinship testing by the Department of
Forensic Sciences in Oslo, Norway.

### Populations included:

- Norway
- Europe
- Africa
- South America
- West Asia
- Middle Asia
- East Asia

A minimum allele frequency of 0.001 was applied in all databases. 
Frequencies below this threshold were adjusted to 0.001.

### Markers

The following markers are included in the databases:

```{r}
norSTR::map50
```


### Installation

```{r, eval = F}
# install.packages("pak")
pak::pkg_install("magnusdv/norSTR")
```
